Classical Planning Algorithms ¡ on the Atari Video Games: Preliminary Results

### 2014-10-31 workshop-paper/paper.tex
Changes to Experimental Section
* Made changes to the text as per Hector's suggestions

$\IW(1)$ outperforms \UCT\ in $4$ out of $9$ games, 
both in terms of  average scores and average times per call. \BFS\ 
is generally faster than $\IW(1)$ but only outperforms \UCT\ in $2$ of the games (\Freeway and
\Seaquest). Compared with the UCT results from  \cite{bellemare:jair2013}, shown in parenthesis, 
$\IW(1)$ still outperforms \UCT\ in $3$  of the  $9$ games (\Breakout, \Enduro~and \Freeway). 
As mentioned in the previous section, the order in which $\IW(1)$ and \BFS\ generate the children
of an expanded node are randomized, something which has a potential effect on the  novelty measures
of nodes, and hence in the search graph. We found that this randomization helps, in particular 
in \Qbert, where not randomizing results  in $\IW(1)$ being trapped into  loops sometimes.

>>>>

$\IW(1)$ outperforms \UCT\ in $4$ out of $9$ games, 
both in terms of  average scores and average times per call. \BFS\ 
is generally faster than $\IW(1)$ but only outperforms \UCT\ in $2$ of the games (\Freeway\ and
\Seaquest). Compared with the \UCT\ results from  \cite{bellemare:jair2013}, shown in parenthesis, 
both $\IW(1)$ and \BFS\ still outperform \UCT\ in $3$  of the  $9$ games (\Breakout, \Enduro\ and \Freeway),
with \BFS\ and \UCT\ tied in another game, \Pong. 
As mentioned in the previous section, the order in which $\IW(1)$ and \BFS\ generate the children
of an expanded node are randomized, something which has a potential effect on the  novelty measures
of nodes, and hence in the search graph. We found that this randomization helps, in particular 
in \Qbert, where not randomizing results  in $\IW(1)$ being trapped into  loops sometimes.
